---
title: "Analysis of COVID-19 patients with Neurological Conditions"
output: rmarkdown::github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/"
)
```

## Install 

You can install the development version of **Phase2.1NeuroRPackage** from GitHub with remotes:

```{r, eval=FALSE}
# install.packages('remotes') # uncomment to install devtools
remotes::install_github('covidclinical/Phase2.1NeuroRPackage',
                        subdir = 'FourCePhase2.1Neuro',
                        upgrade = FALSE)
```

## How to run

The main function `runAnalysis()` has 3 required arguments.
See your site obfuscation parameters (`mask_thres` and `blur_abs`) [here](https://docs.google.com/spreadsheets/d/1Xl9juDBXt86P3xQtsoTaBl2zPl1BIiAG9DI3Rotyqp8/edit#gid=212461777).
If your site does not have race information, set `include_race = FALSE`.

```{r ,eval=FALSE}
library(Phase2.1NeuroRPackage)

runAnalysis(mask_thres = 10, blur_abs = 0, include_race = TRUE)
```

Finally, please submit the results to the central repository:

```{r, eval=FALSE}
submitAnalysis()
```

If you run into any problem adapting this code to your data, let us (@meghutch and @trang1618) know via Slack or [submit an issue](https://github.com/covidclinical/Phase2.1NeuroRPackage/issues/new).

Thank you very much for your support!
